Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-10-26 paper/ms.tex
minor change
explanation for using hayashinos ACF

The survey covered four independent fields. The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies. The second observed region is composed by the fields Subaru/{\it
  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields). The third and
fourth fields are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
$196$ LAEs (1 sub-field), and the field around the Great Observatory
Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
sub-field).

@@

The second constraint is the angular correlation function
(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement}. Instead
we use the results by \cite{Hayashino2004} and
\cite{Ouchi2008,Ouchi2010}. \cite{Hayashino2004} observed in the
densest field of SSA22 while \cite{Ouchi2008} observed a 1 deg$^2$
over the SXDS field, which is twice as large as the SXDS region
observed by \cite{Yamada2012}.

There are some differences between these observations and those by
\cite{Yamada2012}. The details in the color selection, corresponding
limiting luminosities and EW thresholds are different in these
references. Nevertheless we use the ACF from these observations as
additional constraints in spite of the fact that the first selected
models are based only on the surface density statistics by \cite{Yamada2012}.

{\bf The LAEs number density inferred by \cite{Hayashino2004} is
  $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
by \cite{Yamada2012}. In the case of \cite{Ouchi2008} the number
density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
inferred by \cite{Yamada2012} for a portion of the same region.}

@@

From this figure it is clear that the highest density
sub-fields is the only outlier in the distribution. Therefore, using
as a benchmark the number density distribution that includes the
sub-fields in the SSA22 region does not impose a strong bias to select
very rare regions in a cosmological simulation. However, on has to
keep in mind that only very rarely the full number density distribution from a
simulation will include a very dense field as an outlier. We will not
require the presence of such field to judge a mock distribution as
successful. [..]}

>>>>

The survey covered four independent fields:

\begin{enumerate}
\item The first is the SSA22
field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
field has been known to harbor a region with a large density excess of
galaxies. {\bf It is important to note  that the first sub-field of this sample  is
exactly the same that are reported by \cite{Hayashino2004} } as it is reported 
by as by \cite{Yamada2012}  in section $2.1$.

\item The second observed region is composed by the fields Subaru/{\it
  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).

\item The third  field si the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
$196$ LAEs (1 sub-field), and

\item The fourth one is the field around the Great Observatory
Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
sub-field).  
\end{enumerate}

@@

{\bf The second constraint is the angular correlation function
(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for the entire field}. Instead
we use the results by \cite{Hayashino2004} who has reported the ACF for the
first and at the same time the densest sub-field of  SSSA22 as we have mention 
before.

In adition to Hayashino's ACF we use as a matter of comparison the
ACF reported by  \cite{Ouchi2008}. This ACF is computer over
an observed field of 1 deg$^2$ over the SXDS field, which is twice
 as large as the SXDS region observed by \cite{Yamada2012}.

There are some differences between \cite{Ouchi2008} observations and those by
\cite{Yamada2012}. The details in the color selection, corresponding
limiting luminosities and EW thresholds are different in these
references. Nevertheless we use the ACF from this particular to 
get a sense of a mean ACF but do not use it to constrain our parameter space. }

%{\bf The LAEs number density inferred by \cite{Hayashino2004} is
 % $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
%by \cite{Yamada2012}. 
In the case of \cite{Ouchi2008} the number
density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
inferred by \cite{Yamada2012} for a portion of the same region.}

@@

From this figure it is clear that the highest density
sub-fields is the only outlier in the distribution. Therefore, using
as a benchmark the number density distribution that includes the
sub-fields in the SSA22 region does not impose a strong bias to select
very rare regions in a cosmological simulation. However, on has to
keep in mind that only very rarely the full number density distribution from a
simulation will include a very dense field as an outlier. We will not
require the presence of such field to judge a mock distribution as
successful. [...]}
